Digital Analysis of Paintings

### 2014-04-29 paper.tex
Finish paper 12.

The results from the Princeton experiments are promising, but the

>>>>

The results from the Princeton experiments are promising, but the results are
very sensitive to the material of the canvas as well as the tools used, whilst
this might be use for detecting forgeries, there might be situations where this
isn't desired.

The images the authors use are high resolution (800 DPI) and they note that a
lower resolution makes it difficult to decide on the range of scales which are
involved.

The data sets used are relatively small and, although they increase the
knowledge by taking multiple patches from the Van Gogh paintings, but for the
results they show only individual paintings are considered. One could easily
question the validity of their results based on this.

In conclusion this is a very complex but powerful technique which is actually
applying theoretical concepts to perform some interesting analysis and
classification. However, the sensitivity of the technique and with the need for
expert and a posteriori decisions do limit the real application of this
research.
